  \section{Troubleshooting}
  \subsection{Hub or Octopi Issues}
	If you encounter difficulties with the hub or octopi, unplug them 
	from the outlet, then
       plug them back in.  The system is designed to reset itself and re-connect
       after initial set-up is completed.
  \subsection{Nodes}
  \subsubsection{How do I reset the nodes?}
     Turn the switch the the off position and unplug the node. Then plug the node back into the outlet
  and turn the switch to the on position.
  \subsubsection{Node is not connecting to the hub}
  \begin{enumerate}
    \item Ensure the node has the correct wifi credentials. If the default is not
    working make sure the password hasn't been changed.
    \item If the node seems to be connected and isn't communicating, reset the nodes.
  \end{enumerate}
  \subsubsection{Node is connected but no data is being sent from the sensors}
      Make sure the sensors are connected correctly. You can reference the wiring diagrams
     in this manual.

  \subsection{Webpage Issues}
  \subsubsection{Webpage is not loading correctly}
  \begin{enumerate}
    \item Try reloading the webpage.
    \item Try closing the webpage, then reopen the webpage.
    \item If both steps fail to fix your issue, log out of the website, then log back in.
  \end{enumerate}

  \subsection{Other Troubleshooting}
  \subsubsection{If everything else fails?}
    Turn off the node and hub by unplugging both from the outlet, then plug both back into the outlet. The system
     is designed to restart itself and reconfigure automatically once set up.
   \subsection{Acknowledgements}
	3D printer icon made by Flaticon from www.flaticon.com 
